A publishing infrastructure for AI-assisted academic authoring

### 2023-12-26 latex/manuscript.tex
latex: add contributorship statement

TODO: complete

>>>>

M. Pividori and C.S. Greene conceived and designed the study.
M. Pividori designed and implemented the Manubot AI Editor, conducted the prompt engineering, performed the experiments, interpreted the results, and drafted the manuscript.
C.S. Greene supervised the entire project and provided critical guidance throughout the study.
M. Pividori and C.S. Greene revised the manuscript and provided critical feedback.
